---
title: "Introduction to 'scatterPlotMatrix'"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to 'scatterPlotMatrix'}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 7
)
```

```{r setup}
library(scatterPlotMatrix)
```

## Basic usage (dataset uses `factor` type)

```{r}
scatterPlotMatrix(iris)
```

'Species' column is of factor type and has box representation for its categories.

## `zAxisDim` argument (referenced column is categorical)

```{r}
scatterPlotMatrix(iris, zAxisDim = "Species")
```

Each point has a color depending of its 'Species' value.

## `categoricalCS` argument

```{r}
scatterPlotMatrix(iris, zAxisDim = "Species", categoricalCS = "Set1")
```

Colors used for categories are not the same as previously (supported values: Category10, Accent, Dark2, Paired, Set1).

## `zAxisDim` argument (referenced column is continuous)

```{r}
scatterPlotMatrix(iris, zAxisDim = "Sepal.Length")
```

Each point has a color depending of its 'Sepal.Length' value.

## `continuousCS` argument

```{r}
scatterPlotMatrix(iris, zAxisDim = "Sepal.Length", continuousCS = "YlOrRd")
```

Colors used for points are not the same as previously (supported values: Blues, RdBu, YlGnBu, YlOrRd, Reds).

## `corrPlotType` argument

```{r}
scatterPlotMatrix(iris, zAxisDim = "Species", corrPlotType = "Text", corrPlotCS = "YlGnBu")
```

Correlation plots uses simple texts instead of circle tree maps as previously (supported values: Circles, Text)

## Basic usage (dataset doesn't use `factor` type)

```{r}
scatterPlotMatrix(mtcars)
```

Several columns are of numerical type but should be of factor type (for example 'cyl').

## `categorical` argument

```{r}
categorical <- list(NULL, c(4, 6, 8), NULL, NULL, NULL, NULL, NULL, c(0, 1), c(0, 1), 3:5, 1:8)
scatterPlotMatrix(mtcars, categorical = categorical, zAxisDim = "cyl")
```

'cyl' and four last columns have a box representation for its categories (use top slider to see the last three columns).

## `distribType` argument

```{r}
scatterPlotMatrix(iris, zAxisDim = "Species", distribType = 1)
```

Distribution plots are of type 'density plot' (instead of histogram).

## `regressionType` argument

```{r}
scatterPlotMatrix(iris, zAxisDim = "Species", regressionType = 1)
```

Add linear regression plots.

## `rotateTitle` argument

```{r}
scatterPlotMatrix(iris, zAxisDim = "Species", rotateTitle = TRUE)
```

Column names are rotated (can be useful for long column names).

## `columnLabels` argument

```{r}
columnLabels <- gsub("\\.", "<br>", colnames(iris))
scatterPlotMatrix(iris, zAxisDim = "Species", columnLabels = columnLabels)
```

Given names are displayed in place of column names found in dataset; <br> is used to insert line breaks.
